Collaborative Visual Analysis on the Web with RCloud

### 2015-06-23 discussion.tex
reduced text in paragraphs of discussion (collaboration and discovery)

\paragraph*{Discovery is hard} There are several problems.
With hundreds of users and thousands of notebooks, the notebook
tree becomes unwieldy.
The search function does not protect searchers from obsolete and
erroneous notebooks, which by default are retained forever.
It helps with finding notebooks, but not with acquiring
other types of information, such as methodology.

One thing to try is tagging, so that users can mark notebooks
to make them easier to find. However, this relies on users making
a conscious effort, which is not always reliable. It seems better
to rely more on passive metrics, such as how often a notebook has been run.

The system also needs to help users to curate notebooks. If a notebook
has been deleted or superseded by one of its forks, a user who opens it
should be informed. Operations on multiple notebooks and folders of
notebooks should be supported to make curation easier.

\paragraph*{Collaboration is hard}
While forking provides a simple way to continue someone else's work, working
in teams is a lot more complicated. The forking feature is popular but it
poses a problem, too, when dozens of versions of a notebook proliferate.
A possible solution is to allow overwriting the current state
of a notebook with the current state of another fork of the notebook.

Implementing a more general solution seems like a big job.
Even GitHub's web interface does not support merging where there are
conflicts. Unrestricted sharing of notebooks may involve moving
toward git's notion of decentralized code repositories, because GitHub
gists do not support shared ownership.

>>>>

\paragraph*{Discovery is hard} 
With hundreds of users and thousands of notebooks, the notebook tree
becomes unwieldy. The search function does not protect searchers from
obsolete and erroneous notebooks, which by default are retained
forever.  It helps with finding notebooks, but not with finding other
types of metadata. In other words, \emph{textual search} is easy, but
\emph{relevance search} is what we need. Allowing users to \emph{tag}
notebooks is a natural idea, but it relies on users making a conscious
effort, This goes somewhat against our ideal of not asking the user to
do work for the system. Rather, we believe a better alternative is to
have the system work for the user, relying on passive metrics, such as
how often a notebook has been run.  More generally, infrastructure for
automatic \emph{curation} of the software artifacts generated by teams
seems to be an important avenue for future work.

\paragraph*{Collaboration is hard}
While forking provides a simple way to continue someone else's work,
teams working together generate workflows for which forking is not
ideal.  Although popular, forking poses a problem when dozens of
versions of a notebook proliferate. A fully general solution seems
intractable. Nevertheless, we expect future versions of the
notebook infrastructure to move toward git's ideal of decentralized
code repositories, instead of the exclusive ownership mode we
currently employ.
